Singapore's Public Housing Affordability

### 2023-11-14 datastory.qmd
Project Update

<p style="text-align: justify;">
For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at lease earn SGD\$5,230. While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
</p>

@@

<p style="text-align: justify;">
Now let's look at the price increment individually for both years, compared with the same flat type.
</p>

@@

<p style="text-align: justify;">
The interactive graph above compares 
</p>

@@

```{r}

>>>>

<p style="text-align: justify;">
For instance, to afford a 3-room flat, which has a median price of \$360,000, both partners would have to at least earn SGD\$5,230. While it may seem manageable, this does not account for other living expenses, or other income fluctuation - couple may own a car, or have multiple kids.
</p>

@@

<p style="text-align: justify;">
Now let's look at the price increment individually for both years, compared with the same flat type. The graph presented shows a great difference for a 4-room flat between 1990 and 2022. The year 1990 with an average price of SGD$81,525 and 2022 with an average price of SGD$525,092, represented by green and orange respectively. In the graph below, feel free to explore and compare the prices of other flat types between 1990 and 2022! 
</p>

@@

<p style="text-align: justify;">
As mentioned, the rising trend of housing cost, as shown in the graph, indicates that potential owners may face financial barriers when seeking for housing options. Additionally, the graph suggests that the real estate market has become increasingly segmented. Unfortunately, with increasing demand and limited supply, property agents are taking advantage of eager potential home owners (Lam, 2020). 
</p>

<p style="text-align: justify;">
For example, in 2019, a property agent was found guilty of unethical bidding practices in order to cash out a larger commission (Lim, 2019). To curb this, regulatory bodies must enforce strict rules and guidelines to ensure fair practices in this already very competitive and high-stakes market. 
</p>

@@

https://www.todayonline.com/singapore/property-agent-fined-s30000-suspended-12-months-over-unethical-bid-pocket-bigger

https://www.businesstimes.com.sg/property/singapore-property-agents-urged-be-ethical-give-accurate-advice
```{r}
